---
title: "ANA515Assignment2"
author: "Lunhan Zhang"
date: "2022-09-18"
output:
  pdf_document: default
  html_document: default

---


## Section 1: Description of the data. 

This data set contains the data a global time series of case and death data for COVID-19.
It is sourced from JHU CSSE COVID-19 Data as well as The New York Times.
From this data, we will look the trend of death and test-positive and also the comparation by state in US.
This is data is excel csv file.

##Section 2: Reading the data into R. 

```{r}
data <- read.csv("COVID-19 Activity.csv")
```

##Section 3: Clean the data.
```{r, echo = TRUE, results='hide'}
library(dplyr)
smallerdata <- data %>% 
select(PEOPLE_POSITIVE_CASES_COUNT, CONTINENT_NAME, PROVINCE_STATE_NAME, REPORT_DATE, PEOPLE_DEATH_NEW_COUNT, PEOPLE_POSITIVE_NEW_CASES_COUNT, PEOPLE_DEATH_COUNT) %>% 
filter(CONTINENT_NAME=='America') %>%
rename("COUNTRY_NAME"="CONTINENT_NAME")%>%
filter(REPORT_DATE>= ('2022-01-01'))

```

##Section 4: Characteristics of the data.


This dataframe has `r nrow(smallerdata)` rows and `r ncol(smallerdata)` columns. The names of the columns and a brief description of each are in the table below:

```{r}
#this makes a new data.frame called text_tbl with two columns, Names and Description
text_tbl <- data.frame( 
Names = c("PROVINCE_STATE_NAME", "PEOPLE_POSITIVE_NEW_CASES_COUNT", "PEOPLE_DEATH_NEW_COUNT"), 
Description = c("State name for the data", "Number of people were tested positive each day", "Number of people death each day")
) 
text_tbl #prints the table
```

##Section 5: Summary statistics.

```{r}
data_pick3 <- select(smallerdata, PROVINCE_STATE_NAME, PEOPLE_DEATH_NEW_COUNT, PEOPLE_POSITIVE_NEW_CASES_COUNT)
```

```{r, include = TRUE}
Summarytable<-summary(data_pick3) #creates the summary
Summarytable #prints the summary in your output
```
